\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath}
\usepackage[most]{tcolorbox}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhead[L]{Period B Student Performance Briefs}
\fancyhead[R]{Unit 1, Lesson 10}
\fancyfoot[C]{\thepage}

\begin{document}

\begin{center}
{\LARGE \textbf{Period B Student Performance Briefs}}\\[0.05in]
{\large Unit 1 Analysis - Personalized Feedback}\\[0.05in]
\textit{Generated: October 9, 2025}
\end{center}

\vspace{0.15in}

% Edgar (apple_monkey)
\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Edgar} (apple\_monkey) - L10: 6/6 (100\%)]
You show developing skills in Unit 1 concepts with 6/6 correct on L10. Your performance on variable types (0\% correct) indicates this as a priority area for growth. Review the fundamentals of variable types and complete targeted practice problems. Review \textbf{Topic 1-2: The Language of Variation: Variables} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Variable identification and classification
\end{tcolorbox}

\vspace{0.15in}

% Ana (papaya_eagle)
\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Ana} (papaya\_eagle) - L10: 5/6 (83\%)]
You demonstrate solid understanding of measures of spread and normal distribution properties. Your performance on distribution shapes (33\% correct) indicates this as a priority area for growth. Focus on practicing identification and description of symmetric, skewed, and other distribution shapes. Review \textbf{Topic 1-6: Describing the Distribution of a Quantitative Variable} and \textbf{Topic 1-9: Comparing Distributions of a Quantitative Variable} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Distribution shape identification
\end{tcolorbox}

\vspace{0.15in}

% Francois (apricot_horse)
\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Francois} (apricot\_horse) - L10: 6/6 (100\%)]
You show developing skills in Unit 1 concepts with 6/6 correct on L10. Your performance on variable types (0\% correct) indicates this as a priority area for growth. Review the fundamentals of variable types and complete targeted practice problems. Review \textbf{Topic 1-2: The Language of Variation: Variables} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Variable identification and classification
\end{tcolorbox}

\vspace{0.15in}

% Janelle (mango_panda)
\begin{tcolorbox}[colback=yellow!10!white,colframe=orange!75!black,title=\textbf{Janelle} (mango\_panda) - L10: 3/6 (50\%) \textcolor{red}{RED}]
You show good effort tackling constructed response questions, scoring 75\% on the histogram interpretation. Your MC performance at 50\% indicates opportunities to strengthen z-score calculations and normal distributions. Focus on practicing Q02-type problems converting z-scores to proportions using the normal table. Review \textbf{Topic 1-10: The Normal Distribution} for targeted practice.

\vspace{0.1in}
\textbf{Weekend Focus:} Z-score to proportion conversion

\textbf{ACTION REQUIRED:} Complete targeted practice packet (handed out in class)
\end{tcolorbox}

\newpage

% Hazel (apple_rabbit)
\begin{tcolorbox}[colback=yellow!10!white,colframe=yellow!75!black,title=\textbf{Hazel} (apple\_rabbit) - L10: 4/6 (67\%) \textcolor{orange}{YELLOW}]
You attempted both constructed response questions, showing persistence. Your MC performance at 67\% indicates developing understanding of normal distributions. Focus on strengthening your z-score calculations and proportion conversions. Pay special attention to using the normal table correctly for "below" vs. "above" questions. Review \textbf{Topic 1-10: The Normal Distribution} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Normal table usage and z-score calculations
\end{tcolorbox}

\vspace{0.15in}

% Gabriella (guava_cat)
\begin{tcolorbox}[colback=red!10!white,colframe=red!75!black,title=\textbf{Gabriella} (guava\_cat) - L10: 3/6 (50\%) \textcolor{red}{RED}]
You're building foundational skills in Unit 1 statistics. Your performance on z-scores (0\% correct) indicates this as a priority area for growth. Work on calculating z-scores using the formula $z = (x - \mu) / \sigma$ and interpreting what they represent. Review \textbf{Topic 1-10: The Normal Distribution} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Z-score calculation and interpretation

\textbf{ACTION REQUIRED:} Complete targeted practice packet (handed out in class)
\end{tcolorbox}

\vspace{0.15in}

% Keily (apricot_fox)
\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Keily} (apricot\_fox) - L10: 5/6 (83\%)]
You demonstrate solid understanding of measures of center and interpretation in context. Your performance on parameters vs statistics (0\% correct) indicates this as a priority area for growth. Strengthen your ability to distinguish between population parameters ($\mu$, $\sigma$) and sample statistics ($\bar{x}$, $s$). Review \textbf{Topic 1-10: The Normal Distribution} for targeted support.

\vspace{0.1in}
\textbf{Weekend Focus:} Parameters vs. statistics notation
\end{tcolorbox}

\vspace{0.3in}

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!75!black,title=\textbf{How to Use This Brief}]
\begin{enumerate}
    \item \textbf{Identify your status:} Green (≥80\%), Yellow (60-79\%), or Red (<60\%)
    \item \textbf{Note your weekend focus:} This is the single most important skill for you to work on
    \item \textbf{Complete the weekend assignment:} Use Blooket flashcards and review linked topics
    \item \textbf{If you have a packet:} Complete it and bring it to class Tuesday
\end{enumerate}
\end{tcolorbox}

\end{document}
