\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}

\begin{document}

\begin{center}
{\LARGE \textbf{Targeted Practice: Janelle}}\\[0.05in]
{\large Z-Scores \& Normal Distributions}\\[0.05in]
\textit{Focus Skills: Z-score calculations, normal proportions}
\end{center}

\vspace{0.15in}

\begin{tcolorbox}[colback=yellow!10!white,colframe=orange!75!black,title=\textbf{Performance Summary}]
\textbf{MC Score:} 3/6 (50\%) - Red\\
\textbf{Q04 Score:} 3/4 (75\%) - Yellow\\
\textbf{Strengths:} Good CR effort and reasoning\\
\textbf{Focus Areas:} Z-score calculations, normal distribution properties
\end{tcolorbox}

\vspace{0.15in}

\section*{Your Learning Path}

Hi Janelle! You showed excellent effort on the histogram question (Q04), scoring 75\%. This tells me you understand how to interpret distributions. Now let's strengthen your multiple choice skills, especially with z-scores and the normal model.

\textbf{Goal:} Master z-score calculations and normal proportions

\vspace{0.15in}

\section*{Practice Set (5 Items)}

\subsection*{Item 1: Z-Score Calculation}
\textbf{Topic:} Lesson 9 - Z-scores and Standardization

The weights of chocolate bars are normally distributed with mean $\mu = 52$g and standard deviation $\sigma = 1.5$g.

\textbf{Question:} Calculate the z-score for a chocolate bar weighing 49g.

\textbf{Formula Reminder:}
\[
z = \frac{x - \mu}{\sigma}
\]

\textbf{Show your work:}

\vspace{1.5in}

\hrule

\vspace{0.2in}

\subsection*{Item 2: Normal Proportion (Below)}
\textbf{Topic:} Lesson 10 - Working with Normal Distributions

Using the same distribution ($\mu = 52$g, $\sigma = 1.5$g):

\textbf{Question:} What proportion of chocolate bars weigh LESS than 49g?

\textbf{Steps:}
\begin{enumerate}
    \item Calculate z-score (you did this in Item 1!)
    \item Look up z in Table A
    \item The table value IS your proportion
\end{enumerate}

\textbf{Answer:}

\vspace{1.5in}

\hrule

\vspace{0.2in}

\subsection*{Item 3: Normal Proportion (Above)}
\textbf{Topic:} Lesson 10 - Working with Normal Distributions

\textbf{Question:} What proportion of chocolate bars weigh MORE than 55g?

\textbf{Steps:}
\begin{enumerate}
    \item Calculate $z = (55 - 52) / 1.5 = $ \underline{\hspace{1in}}
    \item Look up z in Table A: \underline{\hspace{1in}}
    \item For ``more than'': $1 - \text{(table value)} = $ \underline{\hspace{1in}}
\end{enumerate}

\textbf{Answer:}

\vspace{1.5in}

\hrule

\newpage

\subsection*{Item 4: Empirical Rule Application}
\textbf{Topic:} Lesson 8 - The Normal Model

The weights are still normally distributed with $\mu = 52$g and $\sigma = 1.5$g.

\textbf{Question:} Between what two weights do the middle 95\% of chocolate bars fall?

\textbf{Hint:} Empirical Rule says 95\% fall within $\pm 2$ standard deviations of the mean.

\textbf{Answer:}

\vspace{1.5in}

\hrule

\vspace{0.2in}

\subsection*{Item 5: Interpretation in Context}
\textbf{Topic:} Lesson 10 - Working with Normal Distributions

You found that 2.3\% of chocolate bars weigh more than 55g.

\textbf{Question:} Write one sentence explaining what this means in the context of chocolate bar weights.

\textbf{Answer:}

\vspace{1.5in}

\hrule

\vspace{0.2in}

\section*{Q06 Scaffold: Z-Score Practice (Bonus)}

You didn't attempt Q06 on L10. Let's build up to it!

\subsection*{Q06 Simplified Version}

\textbf{Given:} Reese's cups have $\mu = 48.5$g and $\sigma = 1.2$g

\textbf{Part A:} Calculate z-score for 46g
\[
z = \frac{x - \mu}{\sigma} = \frac{46 - \underline{\hspace{0.5in}}}{\underline{\hspace{0.5in}}} = \underline{\hspace{0.5in}}
\]

\vspace{0.5in}

\textbf{Part B:} Calculate z-score for 51g
\[
z = \frac{51 - \underline{\hspace{0.5in}}}{\underline{\hspace{0.5in}}} = \underline{\hspace{0.5in}}
\]

\vspace{0.5in}

\textbf{Part C:} What proportion fall BETWEEN 46g and 51g?

\textbf{Strategy:}
\begin{enumerate}
    \item Find proportion below 51g: \underline{\hspace{1in}}
    \item Find proportion below 46g: \underline{\hspace{1in}}
    \item Subtract: (proportion below 51g) - (proportion below 46g) = \underline{\hspace{1in}}
\end{enumerate}

\vspace{0.5in}

\newpage

\section*{Success Checklist}

After completing this practice, you should be able to:

\begin{itemize}[label=$\square$]
    \item Calculate z-scores using the formula
    \item Use Table A to find proportions below a z-score
    \item Find proportions above by subtracting from 1
    \item Apply the empirical rule (68-95-99.7)
    \item Interpret statistical results in context
\end{itemize}

\vspace{0.3in}

\section*{Answer Key (Check After Attempting)}

\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Solutions}]

\textbf{Item 1:} $z = (49 - 52) / 1.5 = -2.0$

\vspace{0.1in}

\textbf{Item 2:} $z = -2.0 \rightarrow$ Table A shows 0.0228 $\approx$ 2.3\%

\vspace{0.1in}

\textbf{Item 3:} $z = 2.0 \rightarrow$ Table A shows 0.9772 $\rightarrow$ Above = $1 - 0.9772 = 0.0228 \approx 2.3\%$

\vspace{0.1in}

\textbf{Item 4:} $\mu \pm 2\sigma = 52 \pm 2(1.5) = 52 \pm 3 \rightarrow$ Between 49g and 55g

\vspace{0.1in}

\textbf{Item 5:} ``About 2.3\% of chocolate bars weigh more than 55 grams.'' (or similar)

\vspace{0.1in}

\textbf{Q06 Scaffold:}
\begin{itemize}
    \item Part A: $z = (46 - 48.5) / 1.2 = -2.08$
    \item Part B: $z = (51 - 48.5) / 1.2 = 2.08$
    \item Part C: $0.9812 - 0.0188 = 0.9624 \approx 96\%$
\end{itemize}

\end{tcolorbox}

\vspace{0.2in}

\section*{Next Steps}

\begin{enumerate}
    \item \textbf{Complete this practice} - take your time and show all work
    \item \textbf{Check your answers} - understand any mistakes
    \item \textbf{See your teacher} - get feedback on Q06 scaffold
    \item \textbf{Retake opportunity} - show your improved skills!
\end{enumerate}

\vspace{0.2in}

\begin{center}
\textit{You're already showing strong CR reasoning (75\% on Q04).}\\
\textit{Once you nail z-scores, you'll be in great shape!}
\end{center}

\end{document}
