\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\LARGE \textbf{AP Statistics Period B}}\\[0.1in]
{\Large \textbf{3-Day Weekend Assignment}}\\[0.05in]
{\large Unit 1 Progress Check Preparation}\\[0.05in]
\textbf{Due: Tuesday, October 15, 2025}
\end{center}

\vspace{0.2in}

\begin{tcolorbox}[colback=green!5!white,colframe=green!75!black,title=\textbf{Overview}]
This weekend assignment is differentiated based on your current performance in Unit 1. Your goal is to strengthen specific skills identified in your personalized report before the Progress Check next week.
\end{tcolorbox}

\vspace{0.15in}

\section*{For ALL Students (Everyone completes these)}

\subsection*{Task 1: Review Your Personalized Brief}

\begin{itemize}[leftmargin=*]
    \item Read your individual performance report (handed out in class)
    \item Identify your \textbf{strengths} and \textbf{priority areas for growth}
    \item Note the 1-2 specific skills you need to work on
\end{itemize}

\subsection*{Task 2: Complete Blooket Flashcard Practice}

\begin{itemize}[leftmargin=*]
    \item Access the Unit 1 Review flashcards on our class website/LMS
    \item Complete \textbf{at least TWO 20-minute practice sessions} over the weekend
    \item Focus especially on questions related to your weak skills
    \item \textbf{Tip:} Space out your practice (one session Saturday, one session Sunday) for better retention
\end{itemize}

\subsection*{Task 3: Review Linked Video Resources}

\begin{itemize}[leftmargin=*]
    \item Your brief links to 2 specific Unit 1 topics (e.g., "Topic 1-8: Graphical Representations of Summary Statistics")
    \item Re-watch the videos for those topics on AP Classroom or our class site
    \item Take notes on key concepts you missed
\end{itemize}

\vspace{0.2in}

\section*{For Janelle \& Gabriella (Additional Targeted Practice)}

\begin{tcolorbox}[colback=yellow!10!white,colframe=orange!75!black]
\textbf{Your Priority:} Complete the targeted practice packet I gave you in class.

\begin{itemize}[leftmargin=*]
    \item Work through all 5 practice items
    \item Show your work for each problem
    \item Complete the Q06 scaffold section
    \item Check your answers using the answer key at the end
    \item \textbf{Bring completed packet to class on Tuesday}
\end{itemize}

\textbf{Need Help?} Email me or visit office hours Monday 3-4pm (Room TBD)
\end{tcolorbox}

\vspace{0.2in}

\section*{For Julissa \& Emily (Quiz Completion)}

\begin{tcolorbox}[colback=red!10!white,colframe=red!75!black]
\textbf{Your Priority:} Complete the Unit 1, Lesson 10 Quiz.

\begin{itemize}[leftmargin=*]
    \item Access the quiz on our LMS (link posted in class)
    \item Focus on \textbf{Q04 (histogram)} and \textbf{Q06 (z-scores)} first
    \item These constructed-response questions are required
    \item Show all your work and reasoning
    \item \textbf{Due: Monday night, 11:59pm}
\end{itemize}

\textbf{Reminder:} Constructed response questions let you earn partial credit. Attempt them even if you're not 100\% confident!
\end{tcolorbox}

\vspace{0.2in}

\section*{Success Checklist}

Use this to verify you've completed everything:

\begin{itemize}[label=$\square$,leftmargin=*]
    \item I read my personalized brief and identified my weak skills
    \item I completed at least two 20-minute Blooket practice sessions
    \item I reviewed the video resources linked in my brief
    \item \textit{(If applicable)} I completed my targeted practice packet
    \item \textit{(If applicable)} I finished the L10 quiz with CR questions
\end{itemize}

\vspace{0.2in}

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!75!black,title=\textbf{Why This Matters}]
The Unit 1 Progress Check counts toward your semester grade and tests foundational skills for the entire AP exam. Spending 1-2 hours this weekend on targeted review will significantly improve your performance and confidence.

\textbf{Remember:} Your brief identifies the \textit{exact} skills you need to work on. This isn't busy work---it's a personalized study plan based on data from your actual performance.
\end{tcolorbox}

\vspace{0.2in}

\begin{center}
\textit{Questions? Email me or see me in class Tuesday.}\\
\textit{Have a great long weekend!}
\end{center}

\end{document}
